---
title: "MSU PA Bootcamp Mgmt Comparisons"
author: "Paul Hegedus"
date: "5/19/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
This script contains the analysis to run the simulations of crop responses and net-return for each of the management strategies student groups came up with. This takes some manual editing, where the file name and group name are provided.

**You need to create subfolders in the 'Strategies' folder to store the management strategy shapefile and outputs.**


# Setup
```{r, echo = FALSE}
library(OFPE)
acres <- 158
source("01a_sec1east_models.Rdata") # load the sec1east models
source("02a_comp_fxns.R") # load the functions for below
```


# Groups
## GROUPNAME
```{r}
group_name <- "GROUPNAME"
strat_path <- "/Strategies/GROUPNAME/   ...    "
# run function that performs the sim to predict outcome and makes maps (to strat_path) and outcome table (to Outputs)
TEMPLATE_output <- run_sim(group_name, strat_path)
```


## ...

## ...

# Comparison
First, all of the output files need to be compiled in order to make figures. 

```{r}
list.files("Outputs/")
# combine them/separate them?
# make figures ...
```

