---
title: "MSU PA Bootcamp Mgmt Comparisons"
author: "Paul Hegedus"
date: "6/4/2022"
output: word_document
---

# Introduction
This script runs the code to compare the strategies between the groups and OFPE. The process is to import the output table from each group and compile to make bar charts comparing each strategy.

# Setup
```{r}
library(OFPE)
library(tidyverse)
```

# Import Output Table
```{r}
groups <- list.files("Strategies/")
#groups <- groups[-5]
out_dat <- lapply(groups, 
                  function(x) read.csv(paste0("Strategies/", x, "/Output/", x, "_output_data.csv"))) %>% 
  do.call(rbind, .)

# out_dat <- list(
#   bayne = read.csv(paste0("Strategies/bayne/Output/bayne_output_data.csv")),
#   caleb.trevor.dipiza,
#   Field_Cut,
#   ManagementZone_Sh,
#   Riley_Expert
# )

out_dat$Group <- factor(out_dat$Group)
```

# Make Output Charts
Compare each strategy by creating bar charts for each metric.

## Total Net-Return
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$TotalNR, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = TotalNR)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Total Net-Return ($/field)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(TotalNR, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/TotalNR.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Mean Net-Return
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$MeanNR, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = MeanNR)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Mean Net-Return ($/acre)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(MeanNR, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/MeanNR.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Total Nitrogen
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$TotalN, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = TotalN)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Total N Applied (lbs/field)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(TotalN, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/TotalN.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Mean Nitrogen
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$MeanN, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = MeanN)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Mean N Applied (lbs/acre)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(MeanN, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/MeanN.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Total Yield
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$TotalYld, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = TotalYld)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Total Yield (bu/field)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(TotalYld, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/TotalYld.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Mean Yield
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$MeanYld, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = MeanYld)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Mean Yield (bu/acre)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(MeanYld, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/MeanYld.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```


## Mean Protein
```{r}
MIN <- 0
MAX <- DescTools::RoundTo(max(out_dat$MeanPro, na.rm = T), 5, ceiling)
STEP <- (MAX - MIN) / 10

p <- ggplot2::ggplot(out_dat, ggplot2::aes(x = Group, y = MeanPro)) +
  ggplot2::geom_bar(stat = "identity", position = ggplot2::position_dodge()) +
  ggplot2::scale_y_continuous(name = paste0("Mean Protein (%)"),
                              limits = c(MIN, MAX),
                              breaks = seq(MIN, MAX, STEP)) +
  ggplot2::scale_x_discrete(name = "Strategy") +
  ggplot2::geom_text(data = out_dat,
                     ggplot2::aes(label = round(MeanPro, 1)),
                     position = ggplot2::position_dodge2(1, padding = 1),
                     hjust = "middle",
                     vjust = "bottom") +
  ggplot2::theme_bw() +
  ggplot2::theme(axis.text = ggplot2::element_text(size = 12),
                 legend.text = ggplot2::element_text(size = 12),
                 axis.title = ggplot2::element_text(size = 14),
                 legend.title = ggplot2::element_text(size = 14))
ggplot2::ggsave(paste0("Comparisons/MeanPro.png"),
                        plot = p, device = "png", scale = 1,
                        width = 10, height = 7.5, units = "in")
```



